### 2019-03-17 papers.tex
papers.tex: Track the papers received thus far

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{You know what's a neat form of literature?}

\addtrack
	{Theory}{\textit{Bottles}}
\addpaper
	{Sublinear colorings of 3-colorable graphs in linear time}
	{Thomas Tseng}
	{Keywords: graph coloring, approximation algorithms, analysis of algorithms}
	{SIGBOVIK_2018_paper_3}
	{0cm}
	{}
\addpaper
	{Cubic partitioning of simultaneous antipodal 4-corner-day time spaces}
	{R.\ Welch and G.\ Ray}
	{Keywords: timecube, conspiracy theories, applied mathematics, applied cubism, tuesdays, meridian time, word animals}
	{SIGBOVIK_2018_paper_2}
	{0cm}
	{}
\addpaper
	{Construction of Eulerian trails in large graphs}
	{Stefan Muller and Ben Blum}
	{Keywords: walk, Eulerian trail, large graph}
	{SIGBOVIK_2018_paper_29}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_29}{0cm}
\addpaper
	{Chess circuits}
	{Ross Dempsey, Sydney Timmerman, and Karl Osterbauer}
	{Keywords: chess, logic, boolean circuits}
	{SIGBOVIK_2018_paper_22}
	{2.5cm}
	{}

\addtrack
	{Cryptocurrencies}{\textit{A Dream}}
\addpaper
	{GradCoin:\ A poor-to-poor electronic cash transfer system}
	{Siddhant Jain}
	{Keywords: blockchain, P2P, digital currency}
	{SIGBOVIK_2018_paper_15}
	{0cm}
	{}
\addpaper
	{CommieCoin:\ Seizing the means of crypto-production}
	{Marx van Raasveldt \textit{et al.}}
	{Keywords: communism, crypto-currency, CommieCoin}
	{SIGBOVIK_2018_paper_11}
	{0cm}
	{}
\addpaper
	{That's Numberwangcoin!}
	{Robert J.\ Simmons}
	{Keywords: boredom, lost coins, shouty bits, speculative investment, the number 2 which you may remember from school is deadly to humans}
	{SIGBOVIK_2018_paper_27}
	{1cm}
	{}

\addtrack
	{Stochastic Processes}{\textit{Portrait of Markov}}
\addpaper
	{Ritwik density estimation and analysis using real techniques}
	{Ritwik Gupta, Ritwik Das, and Ritwik Rajendra}
	{Keywords: Ritwik, Council of Ritwiks, population density, statistical analysis, deep learning, state of the art, monte carlo, bayesian methods, real computational methods and statistics}
	{SIGBOVIK_2018_paper_5}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_5}{0cm}
\addpaper
	{On the intractability of multiclass restroom queues with perfect stall etiquette}
	{Sarah Allen and Ziv Scully}
	{Keywords: Markov chain, recursive renewal-reward, poop}
	{SIGBOVIK_2018_paper_30}
	{0cm}
	{}

\addtrack
	{Ayyy Eye}{\textit{Afterimage of a Crimson Eye}}
\addpaper
	{PSYCHO:\ PerSonalitY CHaracterizatiOn of artificial intelligence}
	{Achal Dave and Rohit Girdhar}
	{Keywords: interpretability, psychology, deep learning, artificial intelligence, rorschach}
	{SIGBOVIK_2018_paper_8}
	{0cm}
	{}
\addpaper
	{The NUGGET non-linear piecewise activation}
	{Stephen Merity}
	{Keywords: deep learning, neural networks, nugget, nuggets, chicken nuggets, smart}
	{SIGBOVIK_2018_paper_10}
	{0cm}
	{}
\addpaper
	{Substitute teacher networks:\ Learning with almost no supervision}
	{Samuel Albanie, James Thewlis, and Jo\~ao F.\ Henriques}
	{Keywords: substitute, teacher, networks}
	{SIGBOVIK_2018_paper_28}
	{1cm}
	{}
	\addreview{SIGBOVIK_2018_review_28}{0cm}

\addtrack
	{Parapsychology}{\textit{Get Out of My Head}}
\addpaper
	{This grad student studied parapsychology---and you won't believe what he found}
	{David Edelstein}
	{Keywords: parapsychology, science, experimental design, experimenter effects, philosophy, telepathy}
	{SIGBOVIK_2018_paper_23}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_23}{0cm}

\addtrack
	{Art}{\textit{Open Your Third Eye}}
\addpaper
	{Automating art snobbiness:\ Dead duck or phoenix?}
	{Dion Ysus and Oscar I.\ Hernandez}
	{Keywords: automation, art, elite, 1337 dankster, cicada 3301, de Bruijn sequence}
	{SIGBOVIK_2018_paper_14}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_14}{0cm}
\addpaper
	{Toward a historically faithful performance of the piano works of Anton\'in Qwe\v{r}t\'y}
	{William Gunther and Brian Kell}
	{Keywords: G-flat major, F-sharp minor, A-flat harmonic major $\flat$6 $\flat$5, G-sharp harmonic major $\flat$5}
	{SIGBOVIK_2018_paper_21}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_21}{0cm}
\addpaper
	{WordTeX:\ A WYSIPCTWOTCG typesetting tool}
	{Tom Wildenhain}
	{Keywords: Word, Microsoft Word, LaTeX, WordTeX}
	{SIGBOVIK_2018_paper_12}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_12}{0cm}

\addtocontents{toc}{\protect\pagebreak}

\addtrack
	{Systems}{\textit{Wheel}}
\addpaper
	{mallocd:\ designing a garbage-free nosql data store}
	{igor}
	{Keywords: state-of-the-art, in-memory, garbage-free, cloud-native, nosql, bare metal, containerless, micro-service, data store}
	{SIGBOVIK_2018_paper_4}
	{0cm}
	{}
\addpaper
	{The fluint8 software integer library}
	{Jim McCann and Tom Murphy VII}
	{Keywords: uint8\_t, float, binary32, ieee754}
	{SIGBOVIK_2018_paper_18}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_18}{0cm}
\addpaper
	{A survey of hardware multithreading}
	{Sol Boucher}
	{Keywords: bend, the, kneedle}
	{SIGBOVIK_2018_paper_EasierChair}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_EasierChair}{0cm}
	\addreview{SIGBOVIK_2018_review_EasierChair-2}{0cm}

\addtrack
	{Debugging}{\textit{Amy Likes Spiders}}
\addpaper
	{COBOLd:\ Gobblin' up COBOL bugs for fun and profit}
	{squaresLab and Mr.\ squaresLab SpouseMan}
	{Keywords: software evolution, maintaining software, search-based software engineering, COBOL=\$\$\$\$\$}
	{SIGBOVIK_2018_paper_20}
	{0cm}
	{}
\addpaper
	{Transactional memory concurrency verification with Landslide}
	{Ben Blum}
	{Keywords: landslide terminal, baggage claim, ground transportation, ticketing}
	{SIGBOVIK_2018_paper_13}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_13}{0cm}

\addtrack
	{Programming Languages}{\textit{Save Me}}
\addpaper
	{Dead programming}
	{Michael Coblenz}
	{Keywords: programming languages, live programming, dead programming}
	{SIGBOVIK_2018_paper_25}
	{0cm}
	{}
\addpaper
	{Alternary operators:\ Alternative ternary operators}
	{Jim McCann; Your Name Here; and Your Name Here, Evan}
	{Keywords: ternary, punctuation, operator, punchline}
	{SIGBOVIK_2018_paper_16}
	{0cm}
	{}
\addpaper
	{bashcc:\ Multi-prompt one-shot delimited continuations for Bash}
	{Spencer Baugh and Dougal Pugson}
	{Keywords: control effects, delimited continuations, shell scripting}
	{SIGBOVIK_2018_paper_19}
	{0cm}
	{}
\addpaper
	{Towards a formalization of Claude Shannon's masters thesis}
	{andrewtron3000}
	{Keywords: Coq, proof assistant, formalization, propositional logic, electromechanical relays}
	{SIGBOVIK_2018_paper_7}
	{0cm}
	{}

\addtrack
	{Metaresearch}{\textit{Literature Club}}
\addpaper
	{Heuristic Ordered-Word Longform Obfuscation, Normally Generated, Creating Abstract
	Nominalizations In Monogrammatic Arrangement Keeping Expected Maximum Yield:\ Study Infers
	Greater Breadth Over Vocabularic Initialization Key Property Regarding Extended
	Sesquipedalian Entries; Notably The Abecedarian Tactics Include Overelaboration, Neologisms,
	Textual Interpretations Twisting Lexical Entries By Eliciting Full Online Resources
	Explaining Possible Exchanges; Often Potential Logorrheic Excesses Require Eventual
	Alternate Listing (Instantiating Zeugma); Energetically Iterating Text Strains Jocularity
	Under Starting Thesis Allocating Humor Until Grand Exit After Conclusion Reaches Obvious
	Nadir Yattering Meaninglessly}
	{Luke Breitfeller}
	{Keywords: SIGBOVIK, study of title, title of study}
	{SIGBOVIK_2018_paper_9}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_9}{0cm}
\addpaper
	{Transparency in research}
	{Ryan Kavanagh}
	{Keywords: transparency, opaqueness, big files}
	{SIGBOVIK_2018_paper_26}
	{0cm}
	{}
\addpaper
	{Academic Advancement Advice:\ Author Articles as A.\ A.}
	{A.\ A.}
	{Keywords: AAA, AAAAA, AAAAAAA}
	{SIGBOVIK_2018_paper_24}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_24}{0cm}
\addpaper
	{A definitely not cherry-picked rhetorical analysis of programming languages reviews}
	{Hannah G.\ Ringler and Stefan Muller}
	{Keywords: reviews, academic memes, reviewer two, cherry-picking}
	{SIGBOVIK_2018_paper_17}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_17}{0cm}
\addpaper
	{Is this the shortest SIGBOVIK paper?}
	{Dicong Qiu}
	{Keywords: shortest, SIGBOVIK, paper}
	{SIGBOVIK_2018_paper_1}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_1}{0cm}

>>>>

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{Academic Games}

\addtrack
	{}{Gamification}
\addpaper
	{Aumann agreement by combat}
	{Travis Hance}
	{Keywords: Aumann agreement, combat, agents}
	{SIGBOVIK_2019_paper_18}
	{0cm}
	{}
\addpaper
	{Monetization of development tools for fun and profit}
	{Albin Eldstål-Damlin}
	{Keywords: monetization, micro-transactions, free-to-play, gamification}
	{SIGBOVIK_2019_paper_1}
	{0cm}
	{}

\addtrack
	{}{Let's get this party started!}
\addpaper
	{Elo World: A framework for benchmarking weak chess engines}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: pawn, horse, bishop, castle, queen, king}
	{SIGBOVIK_2019_paper_41}
	{0cm}
	{}
\addpaper
	{A formal treatment of k/n power-hours}
	{Christian Clausen}
	{Keywords: power hour, 2 girls 1 cup, formalized drinking game}
	{SIGBOVIK_2019_paper_4}
	{0cm}
	{}
\addpaper
	{Eventually consistent partying}
	{Veit Heller}
	{Keywords: party system design, buzz factor, SIGBOVIK}
	{SIGBOVIK_2019_paper_17}
	{0cm}
	{}

\addtrack
	{}{Survival advice from a computer scientist}
\addpaper
	{Survival in chessland}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: chess, chess to the death, being a chesspiece to the death}
	{SIGBOVIK_2019_paper_10}
	{0cm}
	{}
\addpaper
	{Optimizing \textit{The Sacrifice}}
	{Nico Zevallos}
	{Keywords: Tarkovsky, \textit{Offret}, film, movie, optimization, path planning, pursuit, evasion, art}
	{SIGBOVIK_2019_paper_13}
	{0cm}
	{}
\addpaper
	{Abusing the RPM package manager to compile software}
	{ILIANA DESTROYER OF WORLDS}
	{Keywords: Linux, software management, recursion}
	{SIGBOVIK_2019_paper_16}
	{0cm}
	{}

\addtrack
	{}{Security and privacy}
\addpaper
	{CVE-2018-90017117}
	{\texttt{t0m7}}
	{Keywords: kingme, exploit, input validation}
	{SIGBOVIK_2019_paper_3}
	{0cm}
	{}
\addpaper
	{Orchhit: User-oblivious social networking}
	{James McCann and Brian Saghy}
	{Keywords: privacy, hashing, cryptography}
	{SIGBOVIK_2019_paper_37}
	{0cm}
	{}

\addtrack
	{}{Machine learning}
\addpaper
	{Color- and piece-blind chess}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: chess, handicaps, man-in-the-middle attacks, neural networks}
	{SIGBOVIK_2019_paper_36}
	{0cm}
	{}
\addpaper
	{Dimensionality-reducing encoding for classification of Pythagorean engendered numbers}
	{Rany Tith and Oscar I.\@ Hernandez}
	{Keywords: number theory, machine learning, encoding, information theory, classification, gender theory, integers, globalization, computation, mathematics}
	{SIGBOVIK_2019_paper_28}
	{0cm}
	{}
\addpaper
	{emojizip: A text compression system based on pictogram-kiloword equivalence}
	{William Gunther and Brian Kell}
	{Keywords: data compression, TensorFlow, [laughing crying emoji]}
	{SIGBOVIK_2019_paper_39}
	{0cm}
	{}
\addpaper
	{Meta-meta-learning for neural architecture search through arXiv Descent}
	{Antreas Antoniou \textit{et al.}}
	{Keywords: meta, meta-meta, deep, NAS}
	{SIGBOVIK_2019_paper_11}
	{0cm}
	{}
\addpaper
	{Towards automatic low hanging fruit identification for the steering of ML research}
	{Nick Frosst and Aidan Gomez}
	{Keywords: machine learning, detection, segmentation, orientation, apple, akee, apricot, avocado, banana, bilberry, blackberry, blackcurrant, black sapote, blueberry, boysenberry, Buddha's hand (fingered citron), crab apples, currant, cherry, cherimoya (custard apple), chico fruit, cloudberry, coconut, cranberry, cucumber, damson, date, dragonfruit (or pitaya), durian, elderberry, feijoa, fig, goji berry, gooseberry, grape, raisin, grapefruit, guava, honeyberry, huckleberry, jabuticaba, jackfruit, jambul, japanese plum, jostaberry, jujube, juniper berry, kiwano (horned melon), kiwifruit, kumquat, lemon, lime, loquat, longan, lychee, mango, mangosteen, marionberry, melon, cantaloupe, honeydew, watermelon, miracle fruit, mulberry, nectarine, nance, olive, orange, blood orange, clementine, mandarine, tangerine, papaya}
	{SIGBOVIK_2019_paper_32}
	{0cm}
	{}

\addtrack
	{}{Architecture: Faster and hotter}
\addpaper
	{Turing-complete chess}
	{Ross Dempsey, Sydney Timmerman, Karl Osterbauer, and Kat Xiang}
	{Keywords: chess, automata, mahogany, Turing machine}
	{SIGBOVIK_2019_paper_26}
	{0cm}
	{}
\addpaper
	{NaN gates and flip FLOPS}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: IEEE 754, mathematics, universal computation, gentleNaN}
	{SIGBOVIK_2019_paper_42}
	{0cm}
	{}
\addpaper
	{HonestNN: an honest neural network "accelerator"}
	{Tim Linscott, Vidushi Goyal, Andrew McCrabb, and Pete Ehrett}
	{Keywords: accelerators, architecture, machine learning, ML, AI, DNN, CNN, graph processing, blockchain, cryptocurrency, 3D printing, security, crowdsourcing, computer, electronics, science, engineering, \#NovelResearch2019, \#BuzzwordsGetCites, \#BetterScience}
	{SIGBOVIK_2019_paper_8}
	{0cm}
	{}
\addpaper
	{Simultaneous microwaving architectures: An efficient scheme for multiplate heating}
	{Charles Yuan}
	{Keywords: high-energy physics, family and consumer sciences, computer architecture, dependent types, machine learning, Byzantine fault tolerance}
	{SIGBOVIK_2019_paper_22}
	{0cm}
	{}
\addpaper
	{Precise ECG platform on modern processors}
	{S.\@ Normalized Infloop and Ivybridge N.\@ Skylake}
	{Keywords: thermal systems, ambient heat modulating technologies, parallel heating, 2D computer graphics, edible content generation}
	{SIGBOVIK_2019_paper_33}
	{0cm}
	{}

\addtrack
	{}{Chess}
\addpaper
	{Is ``Dicong Qiu. Is this the shortest SIGBOVIK paper? From 2018 SIGBOVIK paper'' the shortest SIGBOVIK paper?}
	{Thomas Bach}
	{Keywords: o, o, o}
	{SIGBOVIK_2019_paper_14}
	{0cm}
	{}
\addpaper
	{Is this the tiniest SIGBOVIK paper ever?}
	{Mitchell Jones}
	{Keywords: tiny, zoom, Fermat}
	{SIGBOVIK_2019_paper_5}
	{0cm}
	{}
\addpaper
	{No, this is the tiniest SIGBOVIK paper ever.}
	{Patrick Lin}
	{Keywords: tony, zoom, Mitchell, heart}
	{SIGBOVIK_2019_paper_6}
	{0cm}
	{}
\addpaper
	{Revisiting the shortest SIGBOVIK paper / The revised shortest SIGBOVIK paper}
	{Richard Wardin}
	{Keywords: word golf, revisioned paper, deflation}
	{SIGBOVIK_2019_paper_9}
	{0cm}
	{}

\addtrack
	{}{Simple in theory}
\addpaper
	{A sublinear approximation method for np-hardproblems on limited hardware}
	{Rohan Jhunjhunwala}
	{Keywords: P=NP, approximation methods, hardware}
	{SIGBOVIK_2019_paper_15}
	{0cm}
	{}
\addpaper
	{Simple theoretically practical complexity theory}
	{Ari Cohn}
	{Keywords: complexity theory, constant time, P vs. NP}
	{SIGBOVIK_2019_paper_27}
	{0cm}
	{}

\addtrack
	{}{Languages}
\addpaper
	{A formal semantics of Befunge}
	{Cameron Wong}
	{Keywords: Befunge, semantics, programming languages}
	{SIGBOVIK_2019_paper_24}
	{0cm}
	{}
\addpaper
	{LATEL: A Logical And Transparent Experimental Language}
	{Kelvin M.\@ Liu-Huang}
	{Keywords: conlang, constructed language, phonetics, morphosyntax, set theory, type theory, propositional logic}
	{SIGBOVIK_2019_paper_35}
	{0cm}
	{}
\addpaper
	{GullyNet: Our time will come}
	{Shuby Deshpande}
	{Keywords: AI, hip hop, protest}
	{SIGBOVIK_2019_paper_31}
	{0cm}
	{}

\addtrack
	{}{Error-correcting codes}
\addpaper
	{On double-sided QR codes}
	{Alexey Tikhonov}
	{Keywords: QR codes, steganography, error correction, high capacity, high density, robustness}
	{SIGBOVIK_2019_paper_2}
	{0cm}
	{}
\addpaper
	{Novel defense against code theft using properties of Fibonacci series}
	{Sayan Chaudhry}
	{Keywords: indent, code style, Fibonacci, plagiarism}
	{SIGBOVIK_2019_paper_20}
	{0cm}
	{}
\addpaper
	{Error-detecting RLIRFO data structures for the win}
	{Darío de la Fuente García, Félix Áxel Gimeno Gil, and Juan Carlos Morales Vega}
	{Keywords: error detection, data structures, cosmic rays, stacks, stacks of stacks, stacks of stacks of stacks, template metaprogramming}
	{SIGBOVIK_2019_paper_25}
	{0cm}
	{}

\addtrack
	{}{Measurement studies}
\addpaper
	{Applications of Standard ML at Google}
	{Andrew Benson}
	{Keywords: SML, Standard ML, one-fifty, Harper, Google, software engineering, programming languages}
	{SIGBOVIK_2019_paper_19}
	{0cm}
	{}
\addpaper
	{93\% of Paint Splatters are Valid Perl Programs}
	{Colin McMillen and Tim Toady}
	{Keywords: perl, OCR, regret}
	{SIGBOVIK_2019_paper_34}
	{0cm}
	{}

\addtrack
	{}{Back to the future}
\addpaper
	{Need more RAM? Just invent time travel!}
	{Robert Andrews, Mitchell Jones, Patrick Lin, and the UIUC Theory CS Group}
	{Keywords: complexity, Turing machine, time travel}
	{SIGBOVIK_2019_paper_23}
	{0cm}
	{}
\addpaper
	{On CLI-based Renderers: In which we investigate the utility of rendering teapots in a command line}
	{Michael Sandler}
	{Keywords: teapot, render, speed and performance, command-line interface, CLI, graphics}
	{SIGBOVIK_2019_paper_40}
	{0cm}
	{}
\addpaper
	{SpaceF}
	{Oscar Hernandez and The Space Invaders}
	{Keywords: space, invasion, moonshot, government, \#yeswecandotherightthingandnotgotospace, extraterrestrial intelligence, National Rifle Association, cheese, George Mallary}
	{SIGBOVIK_2019_paper_30}
	{0cm}
	{}

\addtrack
	{}{Pop culture}
\addpaper
	{Which ITG stepcharts are bracket-jumpiest?: In which they milk the $\lceil$A boring follow-up paper to ``Which ITG stepcharts are turniest?'' titled, ``Which ITG stepcharts are crossoveriest and/or footswitchiest?''$\rfloor$ series for all its worth in publication count af}
	{Ben Blum}
	{Keywords: bracket, groove, in, jumps, submission title contains 289 characters which exceeds the maximum allowed length of 255 characters, the}
	{SIGBOVIK_2019_paper_29}
	{0cm}
	{}
\addpaper
	{The computational theory of Lord Voldemort's dark magic}
	{Huilian Sophie Qiu and Hui Yang}
	{Keywords: magic, computing, social good, green computing, Harry Potter, wizarding world, Lord Voldemort, flibbertigibbet}
	{SIGBOVIK_2019_paper_38}
	{0cm}
	{}
\addpaper
	{All you need is dogball}
	{Kai Arulkumaran, Matthew Kelcey, and Andrew Brock}
	{Keywords: dogball, biggan, memes}
	{SIGBOVIK_2019_paper_7}
	{0cm}
	{}
\addpaper
	{On the time complexity of the verification of the factorization of 2\textsuperscript{67}-1}
	{Isaac Grosof and Isaac Grosof}
	{Keywords: algorithms, time complexity, Mersenne prime, history of computation, multiplication}
	{SIGBOVIK_2019_paper_21}
	{0cm}
	{}
